---
title: "Develpment-Economics-Project1"
author: "Mohammad Mostafawi"
date: "11/13/2024"
output: html_document
---

### clothing Industry

# Relevance

The relevance of clothing industry to industrial policies and exchange rate 
fluctuations is somehow interesting. clothing industry in Iran is very 
sensitive to exchange rate. the reason is not beacuse of raw materials 
but is because of smuggling. the point in this industry is that when 
exchange rate is low, smugglers start to import clothing. and when the 
rate of exchange is high, smugglers loose their incentive to import the 
clothing. 





# Economic and Institutional Context

This industry include many low skill and woman workforce in comparison to other 
industries. its overall a labor intensive industry that provide job for many. 
effects on this industry can affect society specially urban densities in many 
ways. 




# Evidence
https://etkfz.com/newsPage?code=65OSy2XeDF

in this link you can read more about is the situation of this industry in response
to fluctuations in exchange rate. 



```{r}

# Load necessary libraries
library(readxl)
library(dplyr)
library(openxlsx)
library(ggplot2)
library(tidyr)
library(patchwork)  
library(stargazer)


# Load the dataset from the Excel file, specifying the correct sheet name
file_path <- "M:/TeIAS/Semester 3/Development Economics/Projects/First Project/all.xlsx"
data <- read_excel(file_path, sheet = "سری زمانی", col_names = FALSE)

# Drop the first row of the dataset
data <- data[-1, ]


# Display the resulting dataset
colnames(data) <- c("year", "industrycode2", "industrycode", "industry", "workshopnumber", "owntaavoni", "ownprivate", "ownpublic", "manageprivate", "managepublic", "workersum", "workermen", "workerwomen", "withwagemen", "withwagewomen", "withoutwagemen", "withoutwagewomen", "compensationservices", "rawmaterial", "rawmaterialimported", "production", "sales", "directexportmilrial", "directexportkdollar", "inputvalue", "outputvalue", "addedvalueofindustry", "nonindustrialservicesrecieved", "nonindustrialservicespayed", "indirecttaxes", "changeininventory", "capitalformation")








```
## Data Summaries 

# Number of Workshops


```{r}

# Filter data for industries with code 14
clothing <- data %>% filter(industrycode == 14)
clothing <- clothing[, !(names(clothing) %in% c("industry"))]
clothing$year <- as.numeric(sub("^13", "", clothing$year))

# Convert all remaining columns to numeric
clothing <- data.frame(lapply(clothing, as.numeric))


ggplot(clothing, aes(x = year, y = workshopnumber)) +
  geom_line() +
  scale_x_continuous(breaks = seq(min(clothing$year), max(clothing$year), by = 1)) +
  labs(title = "Number of Workshops of Clothing Industry", x = "Year", y = "Number of Workshops")




# Reshape the data to long format
clothing_long <- clothing %>%
  pivot_longer(cols = c("ownprivate", "owntaavoni", "ownpublic"), 
               names_to = "OwnershipType", 
               values_to = "NumberOfWorkshops")

# Create the combined plot
ggplot(clothing_long, aes(x = year, y = NumberOfWorkshops, color = OwnershipType)) +
  geom_line() +
  scale_x_continuous(breaks = seq(min(clothing$year), max(clothing$year), by = 1)) +
  labs(
    title = "Comparison of Workshop Numbers in Clothing Industry by Ownership Type",
    x = "Year",
    y = "Number of Workshops",
    color = "Ownership Type"
  ) +
  theme_minimal()


```

as we can see in number of workshops, most of this industry is owned by private sector 
then we can consider this sector mostly a private sector. 


## Number of All Employee by Gender


```{r}



clothing_long <- clothing %>%
  pivot_longer(cols = c("workersum", "workermen", "workerwomen"), 
               names_to = "Gendertype", 
               values_to = "NumberOfWorkers")

# Create the combined plot
ggplot(clothing_long, aes(x = year, y = NumberOfWorkers, color = Gendertype)) +
  geom_line() +
  scale_x_continuous(breaks = seq(min(clothing$year), max(clothing$year), by = 1)) +
  labs(
    title = "Total,men and women workers of clothing industry",
    x = "Year",
    y = "Number of Workers",
    color = "Gendertype"
  ) +
  theme_minimal()




```



```{r}




clothing_long <- clothing %>%
  pivot_longer(cols = c("withwagemen", "withoutwagemen", "withwagewomen","withoutwagewomen"), 
               names_to = "WageStatusofMenandwomen", 
               values_to = "NumberOfWorkers")

# Create the combined plot
ggplot(clothing_long, aes(x = year, y = NumberOfWorkers, color = WageStatusofMenandwomen)) +
  geom_line() +
  scale_x_continuous(breaks = seq(min(clothing$year), max(clothing$year), by = 1)) +
  labs(
    title = "Number of Men and women with and without Wage",
    x = "Year",
    y = "Number of Workers",
    color = "WageStatusofMen"
  ) +
  theme_minimal()



```
There is a very interesting plot since we see that in 81 the percentage of women in the industry is far less than what it is in 90 which they are almost the same. for 93 and 94 
the percentage of women are more than men which is not a common phenomena in Iran's ecnonmy. 









```{r}




clothing_long <- clothing %>%
  pivot_longer(cols = c("production", "sales", "directexportmilrial","capitalformation"), 
               names_to = "MainValues", 
               values_to = "MillionRial")

# Create the combined plot
ggplot(clothing_long, aes(x = year, y = MillionRial, color = MainValues)) +
  geom_line() +
  scale_x_continuous(breaks = seq(min(clothing$year), max(clothing$year), by = 1)) +
  labs(
    title = "Main Values of Clothing Industry",
    x = "Year",
    y = "MillionRial",
    color = "MainValues"
  ) +
  theme_minimal()





```

## Real Values 
in order to make fluctuations in export and production and other important values, we need to consider all of them in real terms. then we use year 80 as base year and adjust all values to real values based on year 80. 
```{r}




inflation <- read_excel("M:/TeIAS/Semester 3/Development Economics/Projects/First Project/inflation.xlsx")

# Ensure the inflation rates are numeric and the year columns match
inflation <- inflation %>% mutate(year = as.numeric(year), inflation = as.numeric(inflation))
inflation$year <- as.numeric(sub("^13", "", inflation$year))

# Merge the inflation dataset with your main clothing dataset by 'year'
clothing <- clothing %>%
  left_join(inflation, by = "year")  # Add inflation rates to clothing data
# Base year (choose the first year in your dataset or a reference year)
base_year <- min(clothing$year)
clothing$inflation <- clothing$inflation / 100

# Calculate the cumulative inflation factor
clothing$CumulativeInflation <- cumprod(1 + clothing$inflation)
clothing$CumulativeInflation <- clothing$CumulativeInflation / clothing$CumulativeInflation[clothing$year == base_year]

# Adjust columns for inflation
adjust_columns <- c("sales", "production", "directexportmilrial", "capitalformation")
clothing[adjust_columns] <- lapply(clothing[adjust_columns], function(column) column / clothing$CumulativeInflation)







```

```{r}



clothing_long <- clothing %>%
  pivot_longer(cols = c("production", "sales", "directexportmilrial","capitalformation"), 
               names_to = "MainValues", 
               values_to = "MillionRial")

# Create the combined plot
ggplot(clothing_long, aes(x = year, y = MillionRial, color = MainValues)) +
  geom_line() +
  scale_x_continuous(breaks = seq(min(clothing$year), max(clothing$year), by = 1)) +
  labs(
    title = "Main Values of Clothing Industry in Real Terms",
    x = "Year",
    y = "MillionRial",
    color = "MainValues"
  ) +
  theme_minimal()
  


```

## Exchange Rate
in this part of analysis, I want to check the effects of exchange rate fluctuations on clothing industry. I need to firstly see that how is these fluctuations. for this I use the data of fluctuations from Daghighe site which is included in package of my analysis. 


```{r}

exchange <- read_excel("M:/TeIAS/Semester 3/Development Economics/Projects/First Project/yearly_exchange_rates_filtered.xlsx")

exchange <- exchange %>% mutate(year = as.numeric(year), exchangerate = as.numeric(exchangerate))

clothing <- clothing %>%
  left_join(exchange, by = "year") 

clothing$real_exchangerate <- clothing$exchangerate / clothing$CumulativeInflation

```
```{r}
ggplot(clothing, aes(x = year, y = real_exchangerate)) +
  geom_line(color = "green", size = 1) +  # Line for real exchange rate
  geom_point(color = "purple", size = 2) +  # Points for each year
  scale_x_continuous(
    breaks = seq(min(clothing$year), max(clothing$year), by = 1)  # Display each year
  ) +
  labs(
    title = "Real Exchange Rate Fluctuations Over the Years",
    x = "Year",
    y = "Real Exchange Rate"
  ) +
  theme_minimal()


```


```{r}

plot1 <- ggplot(clothing, aes(x = year, y = real_exchangerate)) +
  geom_line(color = "green", size = 1) +
  geom_point(color = "purple", size = 2) +
  scale_x_continuous(
    breaks = seq(min(clothing$year), max(clothing$year), by = 1)
  ) +
  labs(
    title = "Real Exchange Rate Fluctuations Over the Years",
    x = "Year",
    y = "Real Exchange Rate"
  ) +
  theme_minimal()

# Prepare data for lower plot (pivot longer for multiple variables)
clothing_long <- clothing %>%
  pivot_longer(cols = c(production, sales, directexportmilrial),
               names_to = "Variable", values_to = "Value")

# Lower plot: Main values (production, sales, directexportmilrial)
plot2 <- ggplot(clothing_long, aes(x = year, y = Value, color = Variable)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  scale_x_continuous(
    breaks = seq(min(clothing$year), max(clothing$year), by = 1)
  ) +
  labs(
    title = "Production, Sales, and Direct Export (Mil Rials) Over the Years",
    x = "Year",
    y = "Values"
  ) +
  theme_minimal()

# Combine plots vertically
combined_plot <- plot1 / plot2
print(combined_plot)



```
As we see in this plot, the main fluctuations happened in 96-97. 
in second plot we see in both this fluctuation, there is an upward 
in production and sales of clothing industry. 
The reason behind this happening is that when exchange rate increases, the smuggling stops and smugglers loose their incentives to smuggle clothing into country. Now in order to show the causality in this process, I need to use a control group and use a dif in dif methodology. The control group for my work I think can be food industry which is not exposed to smuggling and there is no smuggling for it from outside to inside of country. 

## Leather industry as a Control Group

Leather industry 

```{r}
# Filter data for the leather industry (industry code 15)
leather <- data %>% filter(industrycode == 15)

# Drop the "industry" column
leather <- leather[, !(names(leather) %in% c("industry"))]

# Convert year column to numeric (remove prefix 13)
leather$year <- as.numeric(sub("^13", "", leather$year))

# Convert all remaining columns to numeric
leather <- data.frame(lapply(leather, as.numeric))

# Merge the inflation dataset with the leather dataset by 'year'
leather <- leather %>%
  left_join(inflation, by = "year")  # Add inflation rates to leather data

# Base year (choose the first year in the dataset or a reference year)
base_year <- min(leather$year)
leather$inflation <- leather$inflation / 100

# Calculate the cumulative inflation factor
leather$CumulativeInflation <- cumprod(1 + leather$inflation)
leather$CumulativeInflation <- leather$CumulativeInflation / leather$CumulativeInflation[leather$year == base_year]

# Adjust columns for inflation
adjust_columns <- c("sales", "production", "directexportmilrial", "capitalformation")
leather[adjust_columns] <- lapply(leather[adjust_columns], function(column) column / leather$CumulativeInflation)

```
```{r}

plot1 <- ggplot(clothing, aes(x = year, y = real_exchangerate)) +
  geom_line(color = "green", size = 1) +
  geom_point(color = "purple", size = 2) +
  scale_x_continuous(
    breaks = seq(min(clothing$year), max(clothing$year), by = 1)
  ) +
  labs(
    title = "Real Exchange Rate Fluctuations Over the Years",
    x = "Year",
    y = "Real Exchange Rate"
  ) +
  theme_minimal()

# Prepare data for lower plot (pivot longer for multiple variables)
leather_long <- leather %>%
  pivot_longer(cols = c(production, sales, directexportmilrial),
               names_to = "Variable", values_to = "Value")

# Lower plot: Main values (production, sales, directexportmilrial)
plot2 <- ggplot(leather_long, aes(x = year, y = Value, color = Variable)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  scale_x_continuous(
    breaks = seq(min(leather$year), max(leather$year), by = 1)
  ) +
  labs(
    title = "Production, Sales, and Direct Export (Mil Rials) Over the Years For Leather industry",
    x = "Year",
    y = "Values"
  ) +
  theme_minimal()

# Combine plots vertically
combined_plot <- plot1 / plot2
print(combined_plot)

```
```{r}
clothing$industry <- "Clothing"
leather$industry <- "Leather"
combined_data <- bind_rows(clothing, leather)

# Define pre- and post-treatment periods
combined_data <- combined_data %>%
  mutate(
    post_treatment = ifelse(year >= 96, 1, 0),  # Post-treatment indicator
    treated = ifelse(industry == "Clothing", 1, 0)  # Treatment group indicator
  )

# Parallel Trends Plot
ggplot(combined_data, aes(x = year, y = production, color = industry, group = industry)) +
  geom_line(size = 1.2) +
  geom_vline(xintercept = 96.5, linetype = "dashed", color = "red") +
  labs(
    title = "Parallel Trends Before Treatment",
    x = "Year",
    y = "Production (Adjusted for Inflation)",
    color = "Industry"
  ) +
  theme_minimal()

# Difference-in-Differences Regression
did_model <- lm(production ~ post_treatment * treated + post_treatment + treated, data = combined_data)

# Summary Table of Results
stargazer(did_model, 
          type = "latex", 
          title = "Difference-in-Differences Regression Results", 
          label = "tab:did_results",
          dep.var.labels = c("Production"),
          covariate.labels = c("Post-Treatment * Treated", 
                               "Post-Treatment", 
                               "Treated"),
          out = "did_results.tex")

# DiD Effect Visualization
combined_data <- combined_data %>%
  mutate(predicted_production = predict(did_model))

ggplot(combined_data, aes(x = year, y = production, color = industry, group = interaction(industry, post_treatment))) +
  geom_line(size = 1.2, aes(linetype = ifelse(post_treatment == 1, "Post-Treatment", "Pre-Treatment"))) +
  geom_line(aes(y = predicted_production), linetype = "dashed", size = 1) +
  geom_vline(xintercept = 96.5, linetype = "dashed", color = "red") +
  labs(
    title = "Difference-in-Differences Analysis",
    x = "Year",
    y = "Production (Adjusted for Inflation)",
    color = "Industry",
    linetype = "Period"
  ) +
  theme_minimal()

```
## Interpretation of Dif in Dif
The interpretation is this: 
Intercept is 2040886 which is significant and its p value is very small. 
post treatment is -289938 which is not significant and its p value is bigger than what it is happening.
The treated which is the the difference between treatment and control before treatment is significant and its value is -747160.
Post treatment:treated is not significant which shows that after happening treatment, both treatment and control groups are similar and their difference is not significant.

The results suggest that the treatment did not have a statistically significant impact on the production of the clothing industry relative to the leather industry during the analyzed period. Further analysis or alternative control groups may be needed to draw stronger conclusions.








